### 2021-04-13 pldi21/discussion.tex
acks

(Acknowledgements are being prepared and will be included in the version sent to the publisher.)

>>>>

The authors would like to thank
Pavel Panchekha and 
the anonymous POPL 2021 and PLDI 2021 referees 
for thoughtful feedback that has significantly improved this paper. 
This material is based upon work supported by the National Science Foundation 
under Grant No. 1814900 and 1817145.
